\subsection{Ring Homomorphisms}
\begin{definition}
	Given two rings $R,S,$ a function $\phi: R \to S$ is a ring homomorphism if
	\begin{enumerate}[label=\roman*)]
		\item $\phi(a+b) = \phi(a) + \phi(b)$ 
		\item $\phi(ab) = \phi(a)\phi(b)$
		\item $\phi(1_R) = 1_{S}$
	\end{enumerate}
\end{definition}
Notice that, by this definition, we're specifically examining the homomorphism on both operations. The definition of the kernel and image remains invariant under this definition. Furthermore, the property relating to injectivity by way of the kernel criterion remains the same as well.
\begin{proposition}
	Let $\phi : R \to S$ be a ring homomorphism. Then $\ker(\phi)$ is an ideal of $R$.
\end{proposition}
\begin{proof}
	Let $a \in \ker(\phi)$ and $r \in R$. Then 
	\begin{equation*}
		\phi(ar) = \phi(a)\phi(r) = 0\phi(r) = 0, \quad \phi(ra) = \phi(r)\phi(a) = \phi(r)0 = 0
	\end{equation*}
	so $ar,ra \in \ker(\phi)$. Since $\ker(\phi)$ is a subring, it must be true that $\ker(\phi)$ is closed under addition. Thus, $\ker(\phi)$ is an ideal.
\end{proof}



\begin{theorem}[Substitution Principle]
	If $R$ is a ring and $r \in R$, then there exists a ring homomorphism
	\begin{equation*}
		\phi:R[x] \to R, \quad f(x)\mt f(r)
	\end{equation*}
	who's kernel is $(p(x))$, where $p(x)$ is the minimal polynomial satisfied by $r$.
\end{theorem}
\begin{proof}
	Every polynomial $f(x) \in R[x]$ can be written uniquely as
	\[
	f(x) = \sum_{i=0}^n a_i x^i
	\quad \text{with } a_i \in R.
	\]
	Define a map $\Phi : R[x] \to R'$ by
	\[
	\Phi(f) := \sum_{i=0}^n \phi(a_i)\alpha^i.
	\]
	
	This map is well-defined since $\phi(a_i) \in R'$ and $\alpha^i \in R'$, and $R'$ is closed under addition and multiplication. For any $r \in R$ (viewed as a constant polynomial),
	\[
	\Phi(r) = \phi(r),
	\]
	so $\Phi|_R = \phi$. Moreover,
	\[
	\Phi(x) = \phi(1)\alpha = \alpha.
	\]
	
	Now let
	\[
	f(x)=\sum a_i x^i, \quad g(x)=\sum b_i x^i.
	\]
	
	\emph{Additivity:}
	\[
	\begin{aligned}
		\Phi(f+g)
		&= \Phi\!\left(\sum (a_i+b_i)x^i\right) \\
		&= \sum \phi(a_i+b_i)\alpha^i \\
		&= \sum (\phi(a_i)+\phi(b_i))\alpha^i \\
		&= \Phi(f)+\Phi(g).
	\end{aligned}
	\]
	
	\emph{Multiplicativity:}
	\[
	\begin{aligned}
		\Phi(fg)
		&= \Phi\!\left(\sum_k \left(\sum_{i+j=k} a_i b_j\right)x^k\right) \\
		&= \sum_k \phi\!\left(\sum_{i+j=k} a_i b_j\right)\alpha^k \\
		&= \sum_k \sum_{i+j=k} \phi(a_i)\phi(b_j)\alpha^{i+j} \\
		&= \left(\sum_i \phi(a_i)\alpha^i\right)
		\left(\sum_j \phi(b_j)\alpha^j\right) \\
		&= \Phi(f)\Phi(g).
	\end{aligned}
	\]
	
	Thus $\Phi$ is a ring homomorphism. Finally, suppose $\Psi : R[x] \to R'$ is another ring homomorphism such that
	$\Psi|_R = \phi$ and $\Psi(x)=\alpha$. Then for any
	$f(x)=\sum a_i x^i$,
	\[
	\Psi(f)=\sum \Psi(a_i)\Psi(x)^i
	=\sum \phi(a_i)\alpha^i
	=\Phi(f),
	\]
	so $\Psi=\Phi$. Hence $\Phi$ is unique.
\end{proof}
The substitution principle emphasizes the idea that evaluations of polynomials via \textit{substitution} of $x$ with a value $\alpha$ is not random. Every substitution that respects the ring rules is a ring homormophism and in fact, there is exactly one homomorphism for each choice of coefficient map and variable. Now, let $R'=R$, $\phi=\mathrm{id}_R$, and $\alpha=a\in R$ in the Substitution Principle. The resulting homomorphism
\[
\Phi : R[x] \to R
\]
satisfying $\Phi|_R=\mathrm{id}_R$ and $\Phi(x)=a$ is exactly the \emph{evaluation map}
\[
\operatorname{ev}_a(f)=f(a).
\]